Quantifying Sweat Chloride in CF Carriers

### 2025-02-11 Angela Metcalf/quantifying_cl_cf_carriers.qmd
CF carrier interim power

```{r setup}
#| include: false
library(tidyverse)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Angela Metcalf/Quantifying Sweat Chloride in CF Carriers")
```

```{r data cleaning}
#| message: false
df <- read.csv("./Data_Raw/Midpoint data.csv", na.strings = "")
df <- df %>%
  mutate(
    `Right Arm Cl` = as.numeric(Sweat.chloride..right.arm),
    `Left Arm Cl` = as.numeric(Sweat.chloride..left.arm),
    `Right Arm Na` = as.numeric(Sweat.sodium..right.arm),
    `Left Arm Na` = as.numeric(Sweat.sodium..left.arm)
  )
df$`Mean Cl` <- rowMeans(df[, c("Right Arm Cl", "Left Arm Cl")])
df$`Mean Na` <- rowMeans(df[, c("Right Arm Na", "Left Arm Na")])
```

@@

```{r}
ggplot(df,aes(y=`Mean Cl`))+boxplot()
```

>>>>

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(arsenal)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Angela Metcalf/Quantifying Sweat Chloride in CF Carriers")
```

```{r data cleaning}
#| message: false
# Import from REDCap
unlockREDCap(c(rcon = "Sweat Electrolytes in CF Carriers 24-0691"),
  keyring = "API_KEYs",
  envir = 1,
  url = "https://redcap.ucdenver.edu/api/"
)
df <- exportRecordsTyped(rcon)
# Format
df <- df %>%
  mutate(
    `Cl Right` = as.numeric(cl_right), `Cl Left` = as.numeric(cl_left),
    `Na Right` = as.numeric(na_right), `Na Left` = as.numeric(na_left)
  )
df$`Mean Cl` <- rowMeans(df[, c("Cl Right", "Cl Left")])
df$`Mean Na` <- rowMeans(df[, c("Na Right", "Na Left")])
```

# Table 1

```{r}
t1 = tableby(carrier~`Mean Cl` +`Mean Na`,data = df )
summary(t1)
```

@@

```{r}
ggplot(df, aes(x = carrier, y = `Mean Cl`)) +
  geom_boxplot()
```
